Parenting Observation Experiment 2 Lexical Diversity Analysis

### 2019-08-06 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
wrapping up results
edits

d$Condition <- factor(d$condition, levels=c("con","exp"), labels=c("Control","Video"))
save(d, file="Exp2_cleaned_data.Rdata")
```

@@

lex_mean_TTR <- d%>%
  group_by(condition)%>%
  summarise(mean = mean(TTR), sd = sd(TTR))

@@

lex_mean_MTLD <- d%>%
  group_by(condition)%>%
  summarise(mean = mean(MTLD), sd=sd(MTLD))

>>>>

d$Condition <- factor(d$condition, levels=c("con","exp"), labels=c("Control","Video"))
#save(d, file="Exp2_cleaned_data.Rdata")
```

@@

@@
